### 2016-10-13 cv.tex
Switch to 'Source Code Pro' for monospace font
Signed-off-by: Behrooz Nobakht <nobeh5@gmail.com>
Update CV section

% === CV Information
\title{ }
\firstname{Curriculum Vitae}
\familyname{ }
\address{ }{ }{ }
% \phone[mobile]{+31 611 770 610}
\email{behrooz.nobakht@gmail.com}
% \social[twitter]{behruz}
% \social[linkedin]{behrooznobakht}
\extrainfo{Geboren 29-07-1981, Teheran}
% \homepage{LinkedIn}

@@

% Education
\section{Opleiding}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\cventry{2011--2015}{PhD Informatica}{Universiteit Leiden}{Leiden}{}
{\emph{Actors At Work}\copyright}

\cventry{2009--2011}{MSc cum laude Informatica}{Universiteit Leiden}{Leiden}{}{\emph{Deployment of active objects onto multi-core}}

\cventry{1998--2002}{BSc Informatica}{Technologie Universiteit Sharif}{Teheran}{\textit{7.0}}{\emph{Online Shopping}}

% Work Experience
\section{Werkervaring}
% \cventry{year--year}{Job title}{Employer}{City}{}{General description no%
% longer than 1--2 lines.\newline{}%
% Detailed achievements:%
% }

\cventry{2011--Nu}{Senior Software Ontwikkelaar}{SDL Fredhopper}{Amsterdam}{}{Groep leider in cloud\newline}

\cventry{2003--2009}{Medeoprichter en architect}{ASTA Co.}{Teheran}{}{%
\begin{itemize}
\item Het beheer van het bedrijf
\item Ontwikkelen
\item Project onderhandeling
\end{itemize}
}

>>>>

% === CV Information
\title{ }
\firstname{Curriculum Vitae}
\familyname{ }
\address{ }{ }{ }
% \phone[mobile]{+31 611 770 610}
\email{behrooz.nobakht@gmail.com}
% \social[twitter]{behruz}
% \social[linkedin]{behrooznobakht}
\extrainfo{Born 29-07-1981, Tehran, Iran}
% \homepage{LinkedIn}

@@

% Education
\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\cventry{2011--2015}{PhD Computer Science}{Universiteit Leiden}{Leiden}{}
{\emph{Actors At Work}\textcopyright}

\cventry{2009--2011}{MSc cum laude Computer Science}{Universiteit Leiden}{Leiden}{}{\emph{Deployment of active objects onto multi-core}}

\cventry{1998--2002}{BSc Software Engineering}{Sharif University of Technology}{Tehran}{\textit{7.0}}{\emph{Online Shopping}}

% Work Experience
\section{Epxerience}
% \cventry{year--year}{Job title}{Employer}{City}{}{General description no%
% longer than 1--2 lines.\newline{}%
% Detailed achievements:%
% }

\cventry{May 2016}{Lead Software Engineer}{HERE}{Eindhoven}{}{CTO Office Applied Technologies\newline}

\cventry{2011--Apr. 2016}{Senior Software Engineer}{SDL Fredhopper}{Amsterdam}{}{Team Lead -- Cloud Platform\newline}

\cventry{2003--2009}{Co-Founder and Architect}{ASTA Co.}{Tehran}{}{%
\begin{itemize}
\item Software Development and Architecture
\item Project Management
\end{itemize}
}
